Effects of gluon kinematics and the Sudakov form factor on the GBW and BGK saturation models

### 2023-04-21 Paper/draft.tex
plots seem ok
plots to be re-done

\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[a4paper]{geometry}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{breqn}
\usepackage[]{fancyhdr}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{hyperref}
%\usepackage{times}
%\usepackage{merriweather}
%\usepackage{draftwatermark}
\usepackage[backend=biber, style=ieee]{biblatex}

\addbibresource{draft.bib}

@@

\newcommand{\fww}[0]{\mathcal{F}^{\mathrm{WW}}}
\newcommand{\fdp}[0]{\mathcal{F}^{\mathrm{dipole}}}
\newcommand{\sdp}[0]{\sigma_{\mathrm{dipole}}}
\newcommand{\sdpa}[0]{\sigma_{\mathrm{dipole\,Adj.}}}
\newcommand{\GeV}[0]{\mathrm{GeV}}
\newcommand{\comment}[1]{\texttt{\color{red}#1}}
\newcommand{\pairdot}[2]{ \mathbf{#1}\cdot\mathbf{#2}  }
\author{
T.~Goda,$^1$, K.~Kutak$^{1}$ and S.~Sapeta$^1$\\\,\\
$^1$ 
{\small\it The H.\ Niewodnicza\'nski Institute of Nuclear Physics PAN,}\\ 
{\small\it Radzikowskiego 152, 31-342 Krak\'ow, Poland}\\%\,\\
%$^2$ 
%{\small\it Physics Department, Brookhaven National Laboratory,}\\
%{\small\it Upton, NY 11973, USA}\\
}	 
%\title{ New parameters for the Golec-Beiernat--W\"usthoff and Bartels--Golec-Biernat--Kowlski saturation models in the $k_T$-facorization formula of $F_2$}
\title{Effects of gluon kinematics and the Sudakov form factor on the GBW and BGK saturation models}
\date{\today}

@@

%--------------- preprint numbers ---------------------
\vspace{-25em}
\begin{flushright}
%  IFJPAN-IV-2022-16\\
\end{flushright}
\vspace{20em}
%-----------------------------------------------------------------

\begin{abstract}
  We investigate effects of exact gluon kinematics on the parameters of the Golec-Biernat--W\"sthoff, and Bartels--Golec-Biernat--Kowalski models. The resulting parameters show sizable difference, particularly in the normalization $\sigma_0$. The resulting models are applied for the dijet process in DIS to investigate effects of the Sudakov form factor. 
  The result qualitatively agrees with that of Ref.~\cite{vanHameren:2021sqc}, except for the difference stemming from the large-$k_T$ behaviour of the models.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section{Introduction}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\comment{Bibliography will be properly made once the draft is complete. For only now I use biblatex.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\resizebox{0.75\textwidth}{0.25\textwidth}{
\begin{tikzpicture}
\draw[snake=coil,segment aspect=0,segment length=0.1in](-0.875in , 0.5in)--(-0.5in,0.in);
\draw[snake=coil,segment aspect=0,segment length=0.1in](0.875in ,0.5in)--(0.5in,0.in);
\draw(-0.5in , 0in)--(0.5in,0in)--(0.5in , -0.5in)--(-0.5in,-0.5in)--cycle ;

@@

\draw(-0.5in , -0.25in)node[left,scale=0.02in]{$x$, $\kappa$};
\draw(-0.5in , -0.75in)node[left,scale=0.02in]{$x/z$, $k$};
\draw[ snake=coil,segment aspect=1.5,segment length=0.1in](0.5in , -1in)--(0.5in,-0.5in);
\draw[snake=coil,segment aspect=1.5,segment length=0.1in](-0.5in , -1in)--(-0.5in,-0.5in);
\end{tikzpicture}
\begin{tikzpicture}
\draw[snake=coil,segment aspect=0,segment length=0.1in](-0.875in , 0.5in)--(-0.5in,0.in);
\draw[snake=coil,segment aspect=0,segment length=0.1in](0.875in ,0.5in)--(0.5in,0.in);
\draw(-0.5in , 0in)--(0.5in,-0.5in)--(0.5in ,0in)--(-0.5in,-0.5in)--cycle ;

@@

In the small-$x$ region of DIS, interactions are dominated by gluons\cite{Kovchegov:2012mbw}. As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}. 
An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_T^2)$, which is a type of transverse momentum dependent PDFs (TMD PDF)~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}. This appears in the $k_T$-factorization formula~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
The dipole gluon density is also called unintegrated gluon density~(UGD) since it is related to the collinear (integrated) gluon density by
\begin{equation}
xg(x,Q^2)=\int^{Q^2}_0 dk_T^2 \mathcal{F}(x,k^2_t).
\end{equation}
Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.  However, such rise violates unitarity and the Froissart bound~\cite{Kovchegov:2012mbw,Barone:1993sy}. The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth. The phenomenon described by this nonlinear term is called saturation. The meaning of the Froissart bound is that, asymptotically, the cross section can not grow faster than the size of black-disk (proton with high gluon density) which expands like $\ln(s)$~\cite{Badelek:1992gs}.
Despite the success of such evolution equations, there are several popular phenomenological models owing to their simplicity. A notable example is the Golec-Biernat--W\"sthoff saturation model~\cite{Golec-Biernat:1998zce}~(also \cite{Kowalski:2003hm,McLerran:1993ni,Forshaw:1999uf,Iancu:2003ge}). The model was originally proposed in the position space version of the $k_T$-factorization formula, and the object which corresponds to the gluon density of the $k_T$-factorization is called dipole cross section.
In the GBW model, the dipole cross section has the form~\cite{Golec-Biernat:1998zce}
\begin{align}
\sigma_{\mathrm{GBW}}(x,r)&=\sigma_0\left(1-e^{-r^2/R^2_0}\right)&\mathrm{where}&
&R^{-2}_0&=\frac{Q_0^{2}}{4}\left(\frac{x_0}{x}\right)^\lambda.
\end{align}
%\comment{here I use $R_0$ instead of $Q_s$ since for BGK below, $Q_s\neq 1/R_0$. }
The dipole cross section is related to the gluon density by the Fourier transform: 
\begin{equation}
\alpha_s\mathcal{F}(x,k_T^2)=\frac{N_c}{4\pi}\int\frac{d^2\mathbf{r}}{(2\pi)^2}e^{i\mathbf{k}_t\cdot \mathbf{r} }\nabla_{\mathbf{r}}^2\sigma_{\mathrm{dipole}}(x,r).
\label{eq:dipole-gluon}
\end{equation}
%An important feature of the GBW model is that it describes the phenomenon of saturation in a simple form. 
The essence of GBW model is encoded in the $x$-dependent saturation scale $Q_s^2(x)=Q^2_0(x_0/x)^{-\lambda}$, which separates the saturation region and the scaling region.
A further development was made by Bartels, Golec-Biernat and Kowalski~(BGK)~\cite{Bartels:2002cj} which incorporates the DGLAP evolution by modifying the exponent to 
\begin{equation}
R_0^{-2}=\frac{\pi^2\alpha(\mu^2)xg(x,\mu^2)}{3\sigma_0},
\end{equation}
where
\begin{align}
\mu^2&=\frac{C}{r^2}+\mu_0^2 & &\mathrm{and} & xg(x,Q^2_0)&=A_g x^{-\lambda_g}(1-x)^{5.6},
\end{align}
thus improving the description of data at higher $Q^2$.\\
While these models enjoyed much success in phenomenology of DIS, including the diffractive and photo-production processes~\cite{Golec-Biernat:1998zce,Golec-Biernat:1999qor}, as later discussed in detail, derivation of the dipole-factorization formula from the $k_T$-factorization involves with certain simplification and introduction of massive light quarks. 
In the rest of this section, differences of the $k_T$-factorization and the dipole-factorization are outlined.  In Sec.~\ref{Results}, results of the new fit to HERA data in the $k_T$-factorization formula are presented and discussed. In Sec.~\ref{Dijet process at EIC}, we apply the results to compute cross section for the dijet process in DIS at the Electron-Ion Collider (EIC)~\cite{NAP25171} and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\

Let us consider the inclusive DIS process $e p\rightarrow \gamma^* (q) p(p)\rightarrow X$. %where a proton and a photon interact, and their momenta are $p$ and $q$ respectively.
Additionally, let us introduce $q'\equiv q+x p$. 
Then, one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
\begin{align}
    \kappa&=\alpha p-\beta q'+\kappa_t&&\mathrm{and}& k&=a p- bq'+k_T.
\end{align}
For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize, with a change of variable  ${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, in the form~\cite{ Kimber:2001uaa,Kwiecinski:1997ee}
\begin{multline}
	F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_T^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_T^2)\Theta(1-x/z)\\
	\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
	+\left(m_f^2+4Q^2\beta^2(1-\beta)^2\right)\left(\frac{I_3}{2\pi}-\frac{I_4}{2\pi}\right)\right],
	\label{eq:angle-integrated}
\end{multline}
where
\begin{equation}
	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2}.
	\label{eq:z}
\end{equation}
(see Ref.~\cite{ Kimber:2001uaa,Kwiecinski:1997ee} for detail.)
%and
%\begin{equation}
%	\begin{split}
%		\frac{I_1}{2\pi}=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}, &\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},\\
%		\frac{I_3}{2\pi}=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}},&\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},
%	\end{split}
%\end{equation}
%for
%\begin{equation}
%	\begin{split}
%		N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
%		N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_T^2,\\
%		N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_T^2, &\hspace{2cm}
%		N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_T^2.
%	\end{split}
%\end{equation}
%Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_T$-factorizaton formula.
One should note, that gluons are not probed directly, thus the argument of the gluon density is $x/z$ rather than $x$.
If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_T$, 
the above formula can be written in the impact parameter space~\cite{Golec-Biernat:1998zce,Nikolaev:1990ja} (i.e. dipole-factorizaton formula)
\begin{equation}
F_2\left(x,Q^2\right)\sim\int^1_0d\beta \int d^2\mathbf{r}\left|\Psi\left(x,\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(x,r\right),
\label{eq:dipole-factorization}
\end{equation}
where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.\\

The original GBW and BGK models were fitted in the dipole factorization, Eq.~(\ref{eq:dipole-factorization}). In this study, we use Eq.~(\ref{eq:angle-integrated}), where the gluon density is obtained by evaluating Eq.~(\ref{eq:dipole-gluon}).
In order to account for the running coupling, we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is constant for the GBW model, and thus explicitly multiply by running coupling;
\begin{equation}
\alpha_s(\mu^2)\mathcal{F}(x,k_T^2)\rightarrow \alpha_s(\mu)\frac{\alpha_s\mathcal{F}(x,k_T^2)}{0.2},
\end{equation}
where %0.2 is an arbitrary normalization, and 
\begin{equation}
\alpha_s(\mu^2)=\frac{1}{\frac{11 C_A-2n_f}{12\pi}\log\left(\frac{\mu^2}{\Lambda_{\mathrm{QCD}}^2 }\right)},
\end{equation}
and  $\Lambda_{\mathrm{QCD}}^2=0.09\;\GeV^2$.
The factor 0.2 is an arbitrary normalization and the effect is absorbed by $\sigma_0$ and hence, bears no importance.
(For a more detailed analysis of UGD from the BGK model see. Ref.~\cite{Luszczak:2022fkf}\footnote{In Ref.~\cite{Luszczak:2022fkf}, the coupling constant was treated differently, and the large $k_T$-region was matched to the derivative of $xg(x)$, while we have used series transformation to accelerate the high-$k_T$ integration. Their treatment is also different from the original BGK paper~\cite{Bartels:2002cj}. As a consequence their gluon density is positive in the large $k_T$-region and the overall large-$k_T$ behaviour is significantly different.}
)
While there is some ambiguity on what the argument of $\alpha_s(\mu^2)$ should be, we follow Ref.~\cite{Kwiecinski:1997ee} and use
\begin{equation}
	\mu^2=k_T^2+{\kappa'}_t^2+m_f^2+\mu^2_0,
\end{equation}
where we add $\mu^2_0=4\;\GeV^2$ in order to freeze the coupling at low scales.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Results}
\label{Results}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The fit was performed for the following cases
\begin{itemize}
\item GBW model with the fixed coupling in $k_T$-factorization  ($k_T$-GBW),
\item GBW model with the running coupling in $k_T$-factorization (rc-$k_T$-GBW),
\item BGK model in $k_T$-factorization ($k_T$-BGK),
\end{itemize} 
and, as a reference, we provide the following results from Ref.~\cite{Goda:2022wsc};
\begin{itemize}
\item GBW model with massless light quarks in the dipole-factorization ($r$-GBW),
\item GBW model with massive light quarks in the dipole-factorizations ($r$-GBW-massive),
\item  BGK model in  the dipole-factorization ($r$-BGK).
\end{itemize}

>>>>

\documentclass[11pt]{article}
\usepackage[a4paper,left=0.99in, right=0.99in,top=1.2in, bottom=1.2in]{geometry}

\usepackage[english]{babel}
\usepackage[a4paper]{geometry}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{breqn}
\usepackage[]{fancyhdr}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cite}
%\usepackage{times}
%\usepackage{merriweather}
%\usepackage{draftwatermark}
%\usepackage[backend=biber, style=ieee]{biblatex}

%\addbibresource{draft.bib}

@@

\newcommand{\fww}[0]{\mathcal{F}^{\mathrm{WW}}}
\newcommand{\fdp}[0]{\mathcal{F}^{\mathrm{dipole}}}
\newcommand{\sdp}[0]{\sigma_{\mathrm{dipole}}}
\newcommand{\sdpa}[0]{\sigma_{\mathrm{dipole\,Adj.}}}
\newcommand{\GeV}[0]{\mathrm{GeV}}
\newcommand{\comment}[1]{\texttt{\color{red}#1}}
\newcommand{\pairdot}[2]{ \mathbf{#1}\cdot\mathbf{#2}  }
\author{
T.~Goda,$^1$, K.~Kutak$^{1}$ and S.~Sapeta$^1$\\\,\\
$^1$ 
{\small\it The H.\ Niewodnicza\'nski Institute of Nuclear Physics PAN,}\\ 
{\small\it Radzikowskiego 152, 31-342 Krak\'ow, Poland}\\%\,\\
}	 
%\title{ New parameters for the Golec-Beiernat--W\"usthoff and Bartels--Golec-Biernat--Kowlski saturation models in the $k_T$-facorization formula of $F_2$}
\title{Effects of gluon kinematics and the Sudakov form factor on the GBW and BGK saturation models}
\date{\today}

@@

%--------------- preprint numbers ---------------------
\vspace{-25em}
\begin{flushright}
  IFJPAN-IV-2023-XX\\
\end{flushright}
\vspace{20em}
%------------------------------------------------------

\begin{abstract}
We investigate effects of exact gluon kinematics on the parameters of the
Golec-Biernat--W\"sthoff, and Bartels--Golec-Biernat--Kowalski models. The
resulting parameters show sizable difference, particularly in the normalization
$\sigma_0$. The resulting models are applied for the dijet process in DIS to
investigate effects of the Sudakov form factor.  The result qualitatively agrees
with that of Ref.~\cite{vanHameren:2021sqc}, except for the difference stemming
from the large-$k_T$ behaviour of the models.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

\begin{figure}[t]
\centering
\resizebox{0.6\textwidth}{0.2\textwidth}{
\begin{tikzpicture}
  \draw[snake=coil,segment aspect=0,segment length=0.1in](-0.875in , 0.5in)--(-0.5in,0.in);
  \draw[snake=coil,segment aspect=0,segment length=0.1in](0.875in ,0.5in)--(0.5in,0.in);
  \draw(-0.5in , 0in)--(0.5in,0in)--(0.5in , -0.5in)--(-0.5in,-0.5in)--cycle ;

@@

  \draw(-0.5in , -0.25in)node[left,scale=0.02in]{$x$, $\kappa$};
  \draw(-0.5in , -0.75in)node[left,scale=0.02in]{$x/z$, $k$};
  \draw[ snake=coil,segment aspect=1.5,segment length=0.1in](0.5in , -1in)--(0.5in,-0.5in);
  \draw[snake=coil,segment aspect=1.5,segment length=0.1in](-0.5in , -1in)--(-0.5in,-0.5in);
  \end{tikzpicture}
  \hspace{60pt}
  \begin{tikzpicture}
  \draw[snake=coil,segment aspect=0,segment length=0.1in](-0.875in , 0.5in)--(-0.5in,0.in);
  \draw[snake=coil,segment aspect=0,segment length=0.1in](0.875in ,0.5in)--(0.5in,0.in);
  \draw(-0.5in , 0in)--(0.5in,-0.5in)--(0.5in ,0in)--(-0.5in,-0.5in)--cycle ;

@@

In the small-$x$ region of deep intelastic scattering (DIS) process   
%
\begin{equation}
  %\label{eq:}
  e\, p\rightarrow \gamma^* (q)\, p(p)\rightarrow X\,,
\end{equation}
%
where are $p$ and $q$ are, respectively, the momenta of the photon and the
proton, the interactions are dominated by gluons\cite{Kovchegov:2012mbw}. As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}. 
An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_T^2)$, which is a type of transverse momentum dependent PDFs (TMD PDF)~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}. This appears in the $k_T$-factorization formula~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
The dipole gluon density is also called unintegrated gluon density~(UGD) since it is related to the collinear (integrated) gluon density by
\begin{equation}
xg(x,Q^2)=\int^{Q^2}_0 dk_T^2 \mathcal{F}(x,k^2_t).
\end{equation}
Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.  However, such rise violates unitarity and the Froissart bound~\cite{Kovchegov:2012mbw,Barone:1993sy}. The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth. The phenomenon described by this nonlinear term is called saturation. The meaning of the Froissart bound is that, asymptotically, the cross section can not grow faster than the size of black-disk (proton with high gluon density) which expands like $\ln(s)$~\cite{Badelek:1992gs}.
Despite the success of such evolution equations, there are several popular phenomenological models owing to their simplicity.

\comment{Some more general talk like in the previous paper}

\comment{EIC}

In the next section, differences of the $k_T$-factorization and the dipole-factorization are outlined.  In Sec.~\ref{Results}, results of the new fit to HERA data in the $k_T$-factorization formula are presented and discussed. In Sec.~\ref{Dijet process at EIC}, we apply the results to compute cross section for the dijet process in DIS at the Electron-Ion Collider (EIC)~\cite{NAP25171} and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The framework}

A notable example is the Golec-Biernat--W\"sthoff saturation model~\cite{Golec-Biernat:1998zce}~(also \cite{Kowalski:2003hm,McLerran:1993ni,Forshaw:1999uf,Iancu:2003ge}). The model was originally proposed in the position space version of the $k_T$-factorization formula, and the object which corresponds to the gluon density of the $k_T$-factorization is called dipole cross section.
In the GBW model, the dipole cross section has the form~\cite{Golec-Biernat:1998zce}
\begin{align}
\sigma_{\mathrm{GBW}}(x,r)&=\sigma_0\left(1-e^{-r^2/R^2_0}\right)&\mathrm{where}&
&R^{-2}_0&=\frac{Q_0^{2}}{4}\left(\frac{x_0}{x}\right)^\lambda.
\end{align}
%\comment{here I use $R_0$ instead of $Q_s$ since for BGK below, $Q_s\neq 1/R_0$. }
The dipole cross section is related to the gluon density by the Fourier transform: 
\begin{equation}
\alpha_s\mathcal{F}(x,k_T^2)=\frac{N_c}{4\pi}\int\frac{d^2\mathbf{r}}{(2\pi)^2}e^{i\mathbf{k}_t\cdot \mathbf{r} }\nabla_{\mathbf{r}}^2\sigma_{\mathrm{dipole}}(x,r).
\label{eq:dipole-gluon}
\end{equation}
%An important feature of the GBW model is that it describes the phenomenon of saturation in a simple form. 
The essence of GBW model is encoded in the $x$-dependent saturation scale $Q_s^2(x)=Q^2_0(x_0/x)^{-\lambda}$, which separates the saturation region and the scaling region.
A further development was made by Bartels, Golec-Biernat and Kowalski~(BGK)~\cite{Bartels:2002cj} which incorporates the DGLAP evolution by modifying the exponent to 
\begin{equation}
R_0^{-2}=\frac{\pi^2\alpha(\mu^2)xg(x,\mu^2)}{3\sigma_0},
\end{equation}
where
\begin{align}
\mu^2&=\frac{C}{r^2}+\mu_0^2 & &\mathrm{and} & xg(x,Q^2_0)&=A_g x^{-\lambda_g}(1-x)^{5.6},
\end{align}
thus improving the description of data at higher $Q^2$.\\
While these models enjoyed much success in phenomenology of DIS, including the diffractive and photo-production processes~\cite{Golec-Biernat:1998zce,Golec-Biernat:1999qor}, as later discussed in detail, derivation of the dipole-factorization formula from the $k_T$-factorization involves with certain simplification and introduction of massive light quarks.

Additionally, let us introduce $q'\equiv q+x p$. 
Then, one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
\begin{align}
    \kappa&=\alpha p-\beta q'+\kappa_t&&\mathrm{and}& k&=a p- bq'+k_T.
\end{align}
For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize, with a change of variable  ${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, in the form~\cite{ Kimber:2001uaa,Kwiecinski:1997ee}
\begin{multline}
	F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_T^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_T^2)\Theta(1-x/z)\\
	\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
	+\left(m_f^2+4Q^2\beta^2(1-\beta)^2\right)\left(\frac{I_3}{2\pi}-\frac{I_4}{2\pi}\right)\right],
	\label{eq:angle-integrated}
\end{multline}
where
\begin{equation}
	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2}.
	\label{eq:z}
\end{equation}
(see Ref.~\cite{ Kimber:2001uaa,Kwiecinski:1997ee} for detail.)
%and
%\begin{equation}
%	\begin{split}
%		\frac{I_1}{2\pi}=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}, &\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},\\
%		\frac{I_3}{2\pi}=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}},&\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},
%	\end{split}
%\end{equation}
%for
%\begin{equation}
%	\begin{split}
%		N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
%		N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_T^2,\\
%		N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_T^2, &\hspace{2cm}
%		N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_T^2.
%	\end{split}
%\end{equation}
%Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_T$-factorizaton formula.
One should note, that gluons are not probed directly, thus the argument of the gluon density is $x/z$ rather than $x$.
If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_T$, 
the above formula can be written in the impact parameter space~\cite{Golec-Biernat:1998zce,Nikolaev:1990ja} (i.e. dipole-factorizaton formula)
\begin{equation}
F_2\left(x,Q^2\right)\sim\int^1_0d\beta \int d^2\mathbf{r}\left|\Psi\left(x,\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(x,r\right),
\label{eq:dipole-factorization}
\end{equation}
where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.\\

The original GBW and BGK models were fitted in the dipole factorization, Eq.~(\ref{eq:dipole-factorization}). In this study, we use Eq.~(\ref{eq:angle-integrated}), where the gluon density is obtained by evaluating Eq.~(\ref{eq:dipole-gluon}).
In order to account for the running coupling, we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is constant for the GBW model, and thus explicitly multiply by running coupling;
%
\begin{equation}
\alpha_s(\mu^2)\mathcal{F}(x,k_T^2)\rightarrow \alpha_s(\mu)\frac{\alpha_s\mathcal{F}(x,k_T^2)}{0.2},
\end{equation}
where %0.2 is an arbitrary normalization, and 
%
\comment{Question: alphas=0.2}

\begin{equation}
\alpha_s(\mu^2)=\frac{1}{\frac{11 C_A-2n_f}{12\pi}\log\left(\frac{\mu^2}{\Lambda_{\mathrm{QCD}}^2 }\right)},
\end{equation}
and  $\Lambda_{\mathrm{QCD}}^2=0.09\;\GeV^2$.
The factor 0.2 is an arbitrary normalization and the effect is absorbed by $\sigma_0$ and hence, bears no importance.
(For a more detailed analysis of UGD from the BGK model see. Ref.~\cite{Luszczak:2022fkf}\footnote{In Ref.~\cite{Luszczak:2022fkf}, the coupling constant was treated differently, and the large $k_T$-region was matched to the derivative of $xg(x)$, while we have used series transformation to accelerate the high-$k_T$ integration. Their treatment is also different from the original BGK paper~\cite{Bartels:2002cj}. As a consequence their gluon density is positive in the large $k_T$-region and the overall large-$k_T$ behaviour is significantly different.}
)
While there is some ambiguity on what the argument of $\alpha_s(\mu^2)$ should be, we follow Ref.~\cite{Kwiecinski:1997ee} and use
\begin{equation}
	\mu^2=k_T^2+{\kappa'}_t^2+m_f^2+\mu^2_0,
\end{equation}
where we add $\mu^2_0=4\;\GeV^2$ in order to freeze the coupling at low scales.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fits to $F_2$ data}
\label{Results}

@@

The fits were performed for the following cases
\begin{itemize}
\item GBW model with the fixed coupling in $k_T$-factorization  ($k_T$-GBW),
\item GBW model with the running coupling in $k_T$-factorization (rc-$k_T$-GBW),
\item BGK model in $k_T$-factorization ($k_T$-BGK),
\end{itemize} 
and, as a reference, we provide the following results from Ref.~\cite{Goda:2022wsc};
\begin{itemize}
\item GBW model with massless light quarks in the dipole-factorization ($r$-GBW),
\item GBW model with massive light quarks in the dipole-factorizations ($r$-GBW-massive),
\item  BGK model in  the dipole-factorization ($r$-BGK).
\end{itemize}

%-----------------------------------------------------------------------------
\begin{table}[t]
\begin{subtable}{\textwidth}
\center\footnotesize
\input{GBW-parameters.tex}
%\caption{}
\vspace{2mm}
\end{subtable}
\begin{subtable}{\textwidth}
\center\footnotesize
\input{BGK-parameters.tex}
%\caption{}
\vspace{2mm}
\end{subtable}
\caption{Fit parameters of respective models. The parameters of the
dipole-factorization cases are from Ref.~\cite{Goda:2022wsc}.}
\label{tab:table}
\end{table}
%-----------------------------------------------------------------------------

The results of fits are summarized in Tab.~\ref{tab:table}. 
The fit quality of $k_T$-GBW is almost unchanged w.r.t. $r$-GBW, while the rc-$k_T$-GBW shows remarkable improvement, almost halving the $\chi^2$ value.
It was pointed out in Ref.~\cite{Albacete:2004gw,Albacete:2007yr,Albacete:2010sy} that in the BK evolution, the running coupling correction have considerable effects.
% \comment{What is the connection? Their result regarding the 1/x grad of $Q_s$ becoming smaller is clearly not present in our case. If we consider $\mathcal{F}$ with running coupling, it will be a bit bent in very small-x. besides, the analysis of \cite{Albacete:2004gw} extends to around $Y=\ln(x_0/x)\sim35$. for our case it may be just not low enough. (though around $Y=10$, $\alpha_0=0.2$ and running have sizable difference. ) }
Another notable point is that, except for the normalization $\sigma_0$, the parameters are very similar, particularly those of rc-$k_T$-GBW are almost identical to those of $r$-GBW. 
\comment{Describet what's in the figuers...}
